Direct Spectroscopic Detection: A Cheap Method to Detect and Characterize Binary Systems

### 2015-10-08 paper/ms.tex
Updated Section 4.

\begin{figure}
        \centering
        \subfigure[TS23]{
            \label{fig:error:a}
            \includegraphics[scale=0.45]{TS23_simple_Tact2Tmeas.pdf}
         }
         \subfigure[HRS]{
             \label{fig:error:b}
             \includegraphics[scale=0.45]{HET_simple_Tact2Tmeas.pdf}
         }
         \subfigure[IGRINS]{
             \label{fig:error:c}
             \includegraphics[scale=0.45]{IGRINS_simple_Tact2Tmeas.pdf}
         }
         \subfigure[CHIRON]{
             \label{fig:error:d}
             \includegraphics[scale=0.45]{CHIRON_simple_Tact2Tmeas.pdf}
         }
         \caption{Correspondence between the companion temperature measured with the direct spectroscopic detection method, and the actual (literature) values. In all figures, the red dashed line has unity slope, the values with uncertainties are the measurements from the synthetic binary observations (see Section \ref{subsec:systematics}), and the blue lines is the line of best-fit through the data. There is significant bias in all of the measurements except for those using the near-infrared IGRINS instrument.}
         \label{fig:error}
\end{figure}

@@

To measure the impact of both random and systematic noise on the parameter estimation, we made several hundred synthetic binary systems for each instrument used in our program. We made the synthetic binary systems by combining the early-type star spectra from Table \ref{tab:earlycal} with those of the late-type stars in Table \ref{tab:latecal} in every possible combination, provided both observations came from the same instrument. By combining actual observations of early-type and late-type stars, our synthetic binary observations retain any instrument-specific effects that may impact the temperature estimation. We scaled the flux of the late-type star such that the flux ratio between it and the early-type star is ten times the expected flux ratio for main sequence components. The artificial brightening relative to a real binary system is to ensure that the temperature estimation uncertainties are separate from the overall sensitivity of the method (which we discuss in Section \ref{subsec:sensitivity}). We estimate the main sequence flux ratio from the published temperature of the late type star (given in Table \ref{tab:latecal}) and the published spectral types of the primaries available on Simbad \citep{Simbad}, and convert to temperature and luminosity by using Table 5 of \citet{Pecaut2013}.

@@

Each synthetic binary observation contributes a pair of measured and actual temperatures, and so each late-type star in Table \ref{tab:latecal} has many independent temperature measurements made with the direct spectral detection method. To determine the correspondence between measured and actual temperature, we perform an MCMC fit to a straight line using the emcee code \citep{emcee}. We plot the mean and standard deviation of the measured temperatures in Figure \ref{fig:error}, along with 300 MCMC samples for the linear fit and the line of unity slope. The MCMC samples give posterior probability distributions for the parameters $a$ and $b$ relating the actual temperature ($T_a$) to the measured temperature ($T_m$) through

>>>>

\begin{figure}
        \centering
        \subfigure[TS23]{
            \label{fig:error:a}
            \includegraphics[scale=0.45]{TS23_simple_Tact2Tmeas.pdf}
         }
         \subfigure[HRS]{
             \label{fig:error:b}
             \includegraphics[scale=0.45]{HET_simple_Tact2Tmeas.pdf}
         }
         \subfigure[IGRINS]{
             \label{fig:error:c}
             \includegraphics[scale=0.45]{IGRINS_simple_Tact2Tmeas.pdf}
         }
         \subfigure[CHIRON]{
             \label{fig:error:d}
             \includegraphics[scale=0.45]{CHIRON_simple_Tact2Tmeas.pdf}
         }
         \caption{Correspondence between the companion temperature measured with the direct spectroscopic detection method, and the actual (literature) values. In all figures, the red dashed line has unity slope, the values with uncertainties are the measurements from the synthetic binary observations (see Section \ref{subsec:systematics}), and the blue lines are the line of best-fit through the data. There is significant bias in all of the measurements except for those using the near-infrared IGRINS instrument.}
         \label{fig:error}
\end{figure}

@@

To measure the impact of both random and systematic noise on the parameter estimation, we created several hundred synthetic binary systems for each instrument used in our program. We made the synthetic binary systems by combining the early-type star spectra from Table \ref{tab:earlycal} with those of the late-type stars in Table \ref{tab:latecal} in every possible combination, provided both observations came from the same instrument. By combining actual observations of early-type and late-type stars, our synthetic binary observations retain any instrument-specific effects that may impact the temperature estimation. We scaled the flux of the late-type star such that the flux ratio ($F_{\rm secondary}/F_{\rm primary}$) is ten times larger than the expected flux ratio for main sequence components. The artificial brightening relative to a real binary system is to ensure that the temperature estimation uncertainties are separate from the overall sensitivity of the method (which we discuss in Section \ref{subsec:sensitivity}). We estimate the main sequence flux ratio from the published temperature of the late type star (given in Table \ref{tab:latecal}) and the published spectral types of the primaries available on Simbad \citep{Simbad}, and convert to temperature and luminosity by using Table 5 of \citet{Pecaut2013}.

@@

Each synthetic binary observation contributes a pair of measured and actual (literature) companion temperatures, and so each late-type star in Table \ref{tab:latecal} has many independent temperature measurements made with the direct spectral detection method. To determine the correspondence between measured and actual temperature, we perform a Markov Chain Monte Carlo (MCMC) fit to a straight line using the emcee code \citep{emcee}. We plot the mean and standard deviation of the measured temperatures in Figure \ref{fig:error}, along with 300 MCMC samples for the linear fit and the line of unity slope. The MCMC samples give posterior probability distributions for the parameters $a$ and $b$ relating the actual temperature ($T_a$) to the measured temperature ($T_m$) through
